Tango-cc analysis

### 2024-06-12 stats/analysis.Rmd
incorporate co-author feedback

training_trials_plot
saveRDS(training_trials_plot, "../saves/training_trials_plot.rds")
```

@@

```{r combine_plot}
# odd_even_plot <- readRDS("../saves/odd_even_plot.rds")
# stratified_plot <- readRDS("../saves/stratified_plot.rds")
# stratified_agecorrected_plot <- readRDS("../saves/stratified_agecorrected_plot.rds")
# training_trials_plot <- readRDS("../saves/training_trials_plot.rds")

top_row <- ggarrange(
  odd_even_plot,
  stratified_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
  stratified_agecorrected_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
  widths = c(1.7, 1.2, 1.2), 
  nrow = 1,
  labels = c("B", "C", "", "") 
)

ggarrange(
  training_trials_plot,
  top_row,
  nrow = 2,
  heights = c(3, 1.5),
  labels = c("A", "") 
)

ggsave("../figures/tango-cc-results.png", width = 12, height = 11, scale = 0.9, bg = "white")
```

>>>>

training_trials_plot
saveRDS(training_trials_plot, "../saves/training_trials_plot.rds")

ggsave("../figures/tango-cc-variability.png", width = 15, height = 11, scale = 0.7, bg = "white")
```

@@

```{r}
library(ggplot2)
library(ggridges)

# Create example data
data <- data.frame(
  x = rnorm(1000),
  y = as.factor(rep(1:10, each = 100))
)

# Plot using geom_density_ridges
ggplot(data, aes(x = x, y = y)) +
  geom_density_ridges()

```

```{r combine_plot}
odd_even_plot <- readRDS("../saves/odd_even_plot.rds")
stratified_plot <- readRDS("../saves/stratified_plot.rds")
stratified_agecorrected_plot <- readRDS("../saves/stratified_agecorrected_plot.rds")
training_trials_plot <- readRDS("../saves/training_trials_plot.rds")

top_row <- ggarrange(
  odd_even_plot,
  stratified_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
  stratified_agecorrected_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
  widths = c(1.7, 1.2, 1.2), 
  nrow = 1
)

ggsave("../figures/tango-cc-reli.png", width = 12, height = 6, scale = 0.8, bg = "white")

# top_row <- ggarrange(
#   odd_even_plot,
#   stratified_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
#   stratified_agecorrected_plot + theme(axis.text.y = element_blank(), axis.ticks.y=element_blank()), 
#   widths = c(1.7, 1.2, 1.2), 
#   nrow = 1,
#   labels = c("B", "C", "", "") 
# )
# 
# ggarrange(
#   training_trials_plot,
#   top_row,
#   nrow = 2,
#   heights = c(3, 1.5),
#   labels = c("A", "") 
# )
# 
# ggsave("../figures/tango-cc-results.png", width = 12, height = 5, scale = 0.7, bg = "white")
```
